---
title: "Homework 1: ggplot2"
author: "Your Name"
date: "2019-03-04"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
```

By using *mpg* dataset:

1. Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?

- Color
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = displ))
```

- Size
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, size = displ))
```

- Shape
shape can not be applied to continuous variable
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy))
```


2. What happens if you map the same variable to multiple aesthetics?

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = displ, size=displ))
```


3. What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), shape=c(21), stroke = 1)
```

4. What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)?

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = displ< 5))
```
